Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

The first case is that the control of current state is a \texttt{Let} expression,
and its right-hand side is an function application.
By calling function \texttt{atomicEval}, we obtain the closure that callee \texttt{f} stands for.
The successor state's control then transfers to the \texttt{body} expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped \texttt{v} to a fresh address \texttt{addr}.
The new store also extends with \texttt{addr} mapping to the value of \texttt{ae},
which is evaluated from \texttt{atomicEval}.
In the meanwhile, a new frame \texttt{frame} is pushed onto the stack \texttt{k}.
This \texttt{frame} contains the variable name \texttt{x} at left-hand side position of \texttt{Let},
the body expression of \texttt{Let}, and the lexical environment of the body expression.

@@

The structure of function \texttt{step} is similar with concrete CESK machines, 
except non-determinism which makes \texttt{step} returns a list of possible
successor states.
In the beginning of \texttt{step}, we call function \texttt{tick} to update 
the time.
Then we have two cases to consider: 1) Current control expression is \texttt{Let},
and \texttt{App(f, ae)} is being bind to \texttt{x}.
Fristly we retrieve the set of closures that \texttt{f} may represents.
For each closure in the set, we do almost the same as what we did in concrete 
CESK machines. But note that since the continuation is allocated on store (\texttt{kstore}),
a new continuation address \texttt{new_kaddr} is constructed, and a new frame
\texttt{Frame(x, e, env)} paired with the current continuation address \texttt{kaddr}
is joined into this address. Finally, a list of states is generated.

@@

Finally, a user could use function \texttt{analyze} to obtain all possible states 
for a given program.

>>>>

The first case is that the control of current state is a \texttt{Let} expression,
and its right-hand side is an function application.
By calling function \texttt{atomicEval}, we obtain the closure that callee \texttt{f} stands for.
The successor state's control then transfers to the \texttt{body} expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped \texttt{v} to a fresh address \texttt{addr}.
The new store is extended with \texttt{addr} mapping to the value of \texttt{ae},
which is evaluated from \texttt{atomicEval}.
In the meanwhile, a new frame \texttt{frame} is pushed onto the stack \texttt{k}.
This \texttt{frame} contains the variable name \texttt{x} at left-hand side position of \texttt{Let},
the body expression of \texttt{Let}, and the lexical environment of the body expression.

@@

The structure of function \texttt{step} is similar with concrete CESK machines, 
except non-determinism which makes \texttt{step} returns a list of reachable 
successor states.
In the beginning of \texttt{step}, we call function \texttt{tick} to update 
the time.
Then we have two cases to consider: 1) Current control expression is \texttt{Let},
and \texttt{App(f, ae)} is being bind to \texttt{x}.
Fristly we retrieve the set of closures that \texttt{f} may represents.
For each closure in the set, we do almost the same as what we did in concrete 
CESK machines. But note that since the continuation is allocated on store (\texttt{kstore}),
a new continuation address \texttt{new_kaddr} is constructed, and a new frame
\texttt{Frame(x, e, env)} paired with the current continuation address \texttt{kaddr}
is joined into this address. Finally, a list of states is generated.

@@

Finally, a user could use function \texttt{analyze} to obtain all reachable states 
for a given program.
